Boccaccio example: end to end truth for California Current

### 2019-05-24 FullBoccaccioTruthEx.Rmd
add plotting code
Bocaccio example minus true age

```{r plotannage}

@@

# run survey  and sample fish on this for completeness?

# plot it

>>>>

**NOPE! Giving constant output or none. Back to the drawing board on true ages.**

See new file TestCalcZ.Rmd testing `calc_Z` separately and then I will do another separate one testing `calc_stage2age`. Once they work I will update this.

```{r plotannage, eval=FALSE}

@@

# test with one species--this is still full polygon and layer output
trueNatage_ss <- trueNatage[trueNatage$species == "Bocaccio_rockfish",]

# run survey  and sample fish on this for completeness? yes to aggregate
survey_trueNage_ss <- create_survey(dat = trueNatage_ss,
                                 time = timeall,
                                 species = survspp,
                                 boxes = boxall,
                                 effic = effic1,
                                 selex = selex1)

trueNagesamp_ss <- sample_fish(survey_trueNage_ss, effNhigh)

# plot it--first few timesteps for bocaccio

Natageplot <- ggplot(trueNagesamp_ss, aes(x=agecl, y=atoutput)) +
  geom_point() +
  theme_tufte() +
  labs(subtitle = paste(scenario.name,
                        trueNatage_ss$species))
